Perceptions of Corruption in Nigeria

### 2024-12-03 paper/paper.qmd
abstract and literature added

---
title: "Perceptions of Corruption in Nigeria"
subtitle: "Rural Nigerians and Less Educated  Groups Report Higher Corruption"
author: 
  - Fatimah Yunusa
thanks: "Code and data are available at:https://github.com/fatimahsy/Nigeria_Democracy-"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

#install.packages("modelsummary")
#install.packages("rstanarm")
#install.packages("dplyr")
#install.packages("here")
#install.packages("arrow")
#install.packages(tinytable)
library(modelsummary)
library(rstanarm)
library(dplyr)
library(here)
library(arrow)
library(bayesplot)
library(ggplot2)
library(arrow)
library(here)
library(patchwork)

@@

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as
follows. @sec-data....

@@

The data for this study was downloaded, cleaned, analyzed, modeled, and visualized using R [@citeR], a statistical programming language. The following packages were used:

- **`modelsummary`** [@modelsummary]: Used to create well-formatted regression tables and summaries.
- **`rstanarm`** [@rstanarm]: Facilitated Bayesian regression modeling using the Stan backend.
- **`dplyr`** [@dplyr]: Streamlined data manipulation, transformation, and summarization processes.
- **`here`** [@here]: Simplified the organization of file paths, improving project reproducibility.
- **`arrow`** [@arrow]: Enabled efficient handling of large datasets with fast reading and writing capabilities.
- **`bayesplot`** [@bayesplot]: Assisted in producing diagnostic checks and posterior predictive visualizations for Bayesian models.
- **`ggplot2`** [@ggplot2]: Provided extensive tools for creating clear and impactful visualizations.
- **`patchwork`** [@patchwork]: Combined multiple plots into cohesive, professional visuals.
- **`knitr`** [@knitr]: Enabled dynamic report generation, integrating code, output, and text seamlessly.
- **`kableExtra`** [@kableExtra]: Enhanced table styling and formatting for clean, professional presentations.
- **`ggalt`** [@ggalt]: Allowed the creation of specialized plots, enhancing the depth of data visualizations.
- **`haven`** [@haven]: Facilitated the import of `.sav` survey data from the Afrobarometer.
- **`broom.mixed`** [@broommixed]: Streamlined the extraction and tidying of results from mixed models for easy analysis and visualization.
- **`afrobarometer`** [@afrobarometer2023]: Served as the primary data source, providing valuable survey data for analysis.
- **_Telling Stories with Data_** [@tellingstories]: This book was referenced for its code and methodologies.

## Cleaned Data Overview 
```{r}
#| label: tbl-cleaned-data-preview
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| tbl-cap: "Preview of the Cleaned Dataset"

@@

```
The cleaned dataset used in this study is summarised in @tbl-summary-statistics, which provides key statistics to offer an overview of the dataset's structure and characteristics. The most frequent age group among respondents is identified, representing the predominant demographic in terms of age. The table also highlights the urban and male percentages, which indicate the proportion of urban residents (43.38%) and male respondents (49.68%) in the sample.

@@

## Variables of Interest
```{r}
#| label: fig-urban-rural-distribution
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: " Urban vs Rural Respondent Distribution. This bar chart compares the number of respondents residing in urban versus rural areas in Nigeria."

# Plot: Urban vs Rural Respondent Distribution
cleaned_data %>%
  count(URBRUR) %>%
  ggplot(aes(x = URBRUR, y = n, fill = URBRUR)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Urban vs Rural Respondent Distribution",
    x = "Respondent Location",
    y = "Number of Respondents"
  ) +
  theme_minimal() +
  scale_fill_manual(
    values = c("Urban Residents" = "blue", "Rural Residents" = "gray")
  ) +
  guides(fill = "none")

@fig-urban-rural-distribution illustrates the distribution of survey
respondents based on their residential location, categorized as urban or
rural. From this, we see that the sample has more rural residents
compared to urban residents. Specifically, the Afrobarometer survey for
Nigeria, conducted in 2022, reports that approximately 53% of Nigeria's
population resides in rural areas, this is is consistent with national
demographic trends [@worldbank2022rural]. This rural-urban distribution
is important for helping us understand the perspectives seen in the
survey, since rural populations may have different challenges in
governance and corruption compared to urban populations. The imbalance
in representation shows that looking at geographical disparities when
interpreting results from nationwide surveys is important.

```{r}
#| label: fig-corruption-presidency
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Perceived Corruption in the Presidency. This bar chart shows the distribution of respondents' perceptions of corruption in the presidency in Nigeria."

# Plot: Perceived Corruption in the Presidency
cleaned_data %>%
  count(corruption_presidency) %>%
  ggplot(aes(x = corruption_presidency, y = n, fill = corruption_presidency)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Perceived Corruption in the Presidency",
    x = "Perception of Corruption",
    y = "Number of Respondents"
  ) +
  theme_minimal() +
  scale_fill_manual(
    values = c("No Corruption" = "green", 
               "Some Corruption" = "yellow", 
               "High Corruption" = "red", 
               "All Corrupt" = "purple")
  ) +
  guides(fill = "none")

 @fig-corruption-presidency presents the distribution of respondents'
perceptions of corruption within the Nigerian presidency. The variable
"Perceived Corruption in the Presidency" captures respondents'
perceptions of the extent of corruption within the Nigerian presidency
and its officials. This variable originates from Question 38A of the
Afrobarometer survey, which asked: *"How many of the following people do
you think are involved in corruption, or haven’t you heard enough about
them to say: the president and officials in his office?"*
[@Afrobarometer2022codebook] Respondents could choose from the following
values:

-   **0 (None)**: Indicates that the respondent perceives no corruption
    in the office of the presidency.
-   **1 (Some of them)**: Suggests that the respondent believes a few
    individuals in the presidency are involved in corruption.
-   **2 (Most of them)**: Reflects the perception that corruption is
    prevalent among the majority of the presidency's officials.
-   **3 (All of them)**: Suggests the respondent perceives widespread
    corruption, implicating all officials in the presidency.
-   **8 (Refused)**: Indicates the respondent declined to answer the
    question.
-   **9 (Don’t know/Haven’t heard enough)**: Suggests the respondent was
    unsure or lacked sufficient knowledge to provide an answer.
-   **-1 (Missing)**: Represents missing or unavailable responses.

For the analysis, only the substantive responses (0-3) were considered,
in order to help us look into perceptions of corruption within the
presidency. The high frequency of responses in the "High Corruption" and
"Some Corruption" categories reflects persistent concerns about the
integrity of key officials in Nigeria, aligning with broader findings on
corruption in the region. @fig-corruption-presidency presents the
distribution of respondents' perceptions of corruption within the
Nigerian presidency. Among these, the category "High corruption" is the
most frequently reported, followed by "Some corruption". "All corrupt"
ranks third, with "No Corruption" being the least chosen category which
is no surprise given our data is in the context of Nigeria. These
proportions show significant public concern about corruption within the
presidency, consistent with broader trends in public concern abut
corruption corruption within the presidency in Nigeria.

```{r}
#| label: fig-dumbbell-education
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Distribution of Education Levels in Nigeria"
#install.packages("ggalt")
library(ggalt)

cleaned_data %>%
  count(education) %>%
  ggplot(aes(x = n, y = reorder(education, n))) +
  geom_dumbbell(
    aes(xend = 0, x = n), 
    size = 3, colour = "darkblue", dot_guide = TRUE
  ) +
  theme_minimal() +
  labs(
    title = "Distribution of Education Levels in Nigeria",
    x = "Number of Respondents", y = "Education Level"
  )

@fig-dumbbell-education visually represents the educational attainment
levels of respondents in the Afrobarometer survey for Nigeria. The data
reflects responses to the question: *What is your highest level of
education?*. The chart indicates that the most frequent reported level
of education is "secondary school completed," followed by "primary
school completed" and "no formal schooling". Fewer respondents reported
having attained "post secondary qualifications," "university completed,"
or "Post-graduate" education, shows the disparity in advanced
educational attainment across the population. This distribution shows
that basic education levels are more prevalent among respondents, which
may influence their perceptions and responses in the broader survey.
Including educational attainment is important in our analysis because it
is an important socioeconomic factor.

```{r}
#| label: fig-age-group-distribution
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Age Group Distribution. This bar chart displays the number of respondents in each age group in Nigeria."

# Plot: Age Group Distribution
cleaned_data %>%
  count(age_group) %>%
  ggplot(aes(x = age_group, y = n, fill = age_group)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Age Group Distribution",
    x = "Age Group",
    y = "Number of Respondents"
  ) +
  theme_minimal() +
  scale_fill_brewer(palette = "Set3") +
  guides(fill = "none")

@fig-age-group-distribution illustrates the distribution of survey
respondents across five distinct age groups: 18-24, 25-34, 35-44, 45-54,
and 55+. The data reveals that the 25-34 age group is the most
represented, with over 500 respondents, followed by the 35-44 age group.
The youngest cohort, aged 18-24, comprises approximately 300
respondents, while the older age groups (45-54 and 55+) are less
represented in the dataset, with fewer than 200 respondents each. This
distribution highlights a concentration of responses from younger
demographics, particularly those aged 25-34, which may reflect broader
societal trends such as population age structure or survey reach and
accessibility.

## Combined variables of interest?

```{r}
#| label: fig-variables-of-interest
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "combined variables of interest"

library(patchwork)

# Create individual plots
urban_plot <- cleaned_data %>%
  count(URBRUR) %>%
  ggplot(aes(x = URBRUR, y = n, fill = URBRUR)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Urban vs Rural", x = "Location", y = "Count")

corruption_plot <- cleaned_data %>%
  count(corruption_presidency) %>%
  ggplot(aes(x = corruption_presidency, y = n, fill = corruption_presidency)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Corruption Perception", x = "Perception", y = "Count")

education_plot <- cleaned_data %>%
  count(education) %>%
  ggplot(aes(x = n, y = reorder(education, n))) +
  geom_col(fill = "darkblue") +
  theme_minimal() +
  labs(title = "Education Level", x = "Count", y = "Education")

age_plot <- cleaned_data %>%
  count(age_group) %>%
  ggplot(aes(x = age_group, y = n, fill = age_group)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Age Distribution", x = "Age Group", y = "Count")

# Combine plots
urban_plot + corruption_plot + education_plot + age_plot +
  plot_layout(ncol = 2)

## Corruption Perceptions Vs Variables of Interest 
```{r}
#| label: fig-education-vs-corruption
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Relationship between Education Levels and corruption percetpions in Nigeria  in Nigeria"

@@

This heatmap in @fig-education-vs-corruption shows the relationship between respondents’ education levels and their perceptions of corruption in Nigeria. The x-axis represents corruption perception categories (All Corrupt, High Corruption, No Corruption, and Some Corruption), while the y-axis represents education levels, ranging from No Formal Schooling to Post-graduate. The intensity of the color reflects the number of respondents, with darker shades indicating higher counts.

The heatmap reveals that respondents who completed secondary school or some secondary schooling dominate the High Corruption and Some Corruption categories. Respondents with higher education levels (university and post-graduate) are distributed more evenly across the corruption perception categories, with fewer concentrated in any specific category. Conversely, respondents with no formal schooling or only informal education are sparsely represented across all categories.

This visualization highlights a notable concentration of corruption perceptions among respondents with mid-level education (secondary schooling), while those with higher education tend to have more varied perceptions. These findings suggest a potential link between educational attainment and experiences or attitudes toward corruption, particularly among those with secondary-level education.

@@

```
@fig-age-versus-corruption shows the relationship between respondents' age group and their perceptions of corruption in Nigeria. Each panel corresponds to one of four corruption perception levels: * All Corruption, High Corruption, Some Corruption, and No Corruption.*Whitin each panel, the bars represent the count of respondent across five age groups (18-24, 25-34, 35-44, 45-54, and 55+), enabling a clear comparison of how perceptions vary by age.

The 25–34 and 35–44 age groups have the highest counts in the High Corruption and Some Corruption categories, suggesting that middle-aged respondents are more likely to perceive corruption as significant. In contrast, younger respondents (18–24) and older respondents (55+) report lower levels of corruption perception in these categories.

In the All Corrupt category, the 25–34, 35–44, and 55+ age groups dominate, while the 18–24 and 45–54 groups have lower counts. The No Corruption category has low counts across all age groups, indicating that very few respondents, regardless of age, perceive the absence of corruption.

@@

# Convert corruption_presidency to numeric if needed
cleaned_data$corruption_numeric <- as.numeric(factor(cleaned_data$corruption_presidency))

```
The relationship between respondents' residential location (rural vs. urban) and their perceptions of corruption is shown in @fig-ruralurban-versus-corruption Each bar represents the proportion of respondents within rural and urban groups who hold different corruption perceptions: All Corrupt, High Corruption, Some Corruption, and No Corruption.

@@

These findings indicate that residential location does not significantly influence corruption perceptions, as rural and urban respondents report similar distribution patterns across all categories. The results suggest that perceptions of corruption are pervasive and relatively consistent across geographic locations.

@@

```
@fig-gender-versus-corruption shows the the relationship between respondents' gender (male and female) and their perceptions of corruption. Each panel represents one gender, displaying the count of respondents across four corruption perception categories: All Corrupt, High Corruption, Some Corruption, and No Corruption.

@@

These results suggest that gender does not significantly influence perceptions of corruption, as male and female respondents exhibit similar distribution patterns across all perception categories. The findings highlight a shared acknowledgment of corruption as a major issue across genders in Nigeria.

@@

# Results

@@

The analysis revealed distinct trends in Corruption perceptions in
different demographics. Our results are summarized in @tbl-modelresults.This presents the estimated coefficients and standard
errors for each predictor included in the model. The dependent variable
is the perception of corruption in the presidency, categorized into
ordered levels. The table includes predictors such as education level,
gender, urban or rural location, and agre group, which are modeled to
explain variations in corruption perceptions. Each predictor's
coefficient represents its effect on the log odds of perceiving
corruption in the presidency at a specific level relative to lower
levels, holding other variables constant.

@@

# Discussion

This paper looks into public perceptions of corruption within the Nigerian Presidency, using data from Afrobarometer Round 9 survey. A bayesian ordinal logistic regression model was used to evaluate the influence of demographic variables like education, gender, urban/rural residence, and age group on corruption perceptions. We found that higher education levels, urban residency, and gender play significant roles in shaping perceptions, with educated and urban individuals more likely to perceive high levels of corruption in Nigeria.

## The Role of Education in Shaping Corruption Perceptions {#sec-first-point}

## Urban-Rural Disparities in Perception

## Gender Dynamics in Corruption Perception

@@

@@

Weaknesses and next steps should also be included.

@@

@@

@@

# Posterior Predictive Check
pp_check(bayesian_model) +
  theme_classic() +
  labs(
    title = "Posterior Predictive Check",
    x = "Observed Data",
    y = "Density"
  )

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-diagnostic-ppcheck
#| fig-cap: "Posterior Predictive Check for the Bayesian ordinal logistic regression model."

# Posterior Predictive Check
pp_check(bayesian_model) +
  theme_classic() +
  labs(
    title = "Posterior Predictive Check",
    x = "Observed Data",
    y = "Density"
  )

>>>>

---
title: "Perceptions of Corruption in Nigeria"
subtitle: "Rural Nigerians and Less Educated  Groups Report Higher Corruption"
author: 
  - Fatimah Yunusa
thanks: "Code and data are available at:https://github.com/fatimahsy/Nigeria_Democracy-"
date: today
date-format: long
abstract: "Peceptions of corruption in the Nigerian presidency vary significantly across demogrpahic groups. Using Afrobarometer survey data and Bayesisan ordinal logistic regression, this study looks at how education, gender, age, and urban versus rural residence influence these perceptions. The results show that urban residents and yourger individuals are more likely to perceive high corruption, while rura populations and those with higher education show views that are moderate. These results show the need for targeted anti-corruption campaigns to adress demographic differences and imporve governance accountability in Nigeria"
format: pdf
toc: true
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

#install.packages("modelsummary")
#install.packages("rstanarm")
#install.packages("dplyr")
#install.packages("here")
#install.packages("arrow")
#install.packages("tinytable")
library(modelsummary)
library(rstanarm)
library(dplyr)
library(here)
library(arrow)
library(bayesplot)
library(ggplot2)
library(arrow)
library(here)
library(patchwork)

@@

Corruption is a very big challenge to governance and development in Nigeria as a result of its ability to undermine public trust and economic growth. As the United Nations Office on Drugs and Crime (UNODC) stated, "corruption affects the lives of ordinary Nigerian, impeding development and eroding public trust in institutions [@corruptionsurvey2024]. This paper looks into the role of demographic factors-education,gender,age, and urban versus rural residence-in shaping perceptions of corruption in the Nigerian presidency.

Primarily, this paper is aimed at understanding how different demographic groups perceive corruption in the Nigerian presidency and to identify ways thiis can help improve anti-corruption campaigns, While existing studies have largely been focused on the institutional dynamics, there seems to be a lack of demographic-specific analysis within the Nigerian context. This paper addresses this gap by making these demographics the focus. It does this by using nationally representative data from Afrobarometer [@afrobarometer2023], a leading survey initiative capturing public attitudes on governance, democracy, and corruption across Africa. A Bayesian ordinal logistic regression was used to find patterns in how education, gender, age, and geographic location influence perceptions of corruption.

Our paper shows that there are alot of disparities in corruption perceptions across demographic groups. Younger respondents and urban residents have higher perceptions of corruption, likely because of higer exposure to investigative media and political discourse. In contrast, rural populations-often reliant on patronage systems- tend to report more neutral views. Education also plays an important role since we find that secondary school graduates have the highest corruption perceptions.

Understanding these demographic differences is important for designing effective anti-corruption campaigns. Making sure outreach efforts are tailored to the unique experiences and perceptions of different demographic groups can increase their effectiveness and increase public trust. For example, youth-focused campaigns that leverage social media platforms and urban outreach using investigative journalism can engage the people. At the same time, localized, culturally appropriate campaigns in rural areas can address the different needs of these populations. A the UNODC emphasizes, 'targeted and effective anti-corruption policies will improve likes of Nigerian citizens" [@afrobarometer2023].

The remainder of this paper is structured as follows; @sec-data detailed the data used for this paper, @sec-model introduces the Bayesian ordinal logistic regression model used to study the relationship between our variables of interest. @sec-results presents the findings from the model, detailing how different demographic factors like education and age affect corruption perception in Nigeria. @sec-discussion examines these results, discussing their implications for anti-corruption policies, weaknesses and next steps. @sec-survey-appendix explores the details of the Afrobarometer survey. @sec-model-details shows plots for Posterior predictive checks and Diagnostics as well as their analysis.

@@

The data for this study was downloaded, cleaned, analyzed, modeled, and
visualized using R [@citeR], a statistical programming language.[@afrobarometer2023] served as the primary data source, providing valuable survey data for analysis.***Telling Stories with Data*** [@tellingstories] was referenced for its code and methodologies. The
following packages were used:

-   **`modelsummary`** [@modelsummary]: Used to create well-formatted
    regression tables and summaries.
-   **`rstanarm`** [@rstanarm]: Facilitated Bayesian regression modeling
    using the Stan backend.
-   **`dplyr`** [@dplyr]: Streamlined data manipulation, transformation,
    and summarization processes.
-   **`here`** [@here]: Simplified the organization of file paths,
    improving project reproducibility.
-   **`arrow`** [@arrow]: Enabled efficient handling of large datasets
    with fast reading and writing capabilities.
-   **`bayesplot`** [@bayesplot]: Assisted in producing diagnostic
    checks and posterior predictive visualizations for Bayesian models.
-   **`ggplot2`** [@ggplot2]: Provided extensive tools for creating
    clear and impactful visualizations.
-   **`patchwork`** [@patchwork]: Combined multiple plots into cohesive,
    professional visuals.
-   **`knitr`** [@knitr]: Enabled dynamic report generation, integrating
    code, output, and text seamlessly.
-   **`kableExtra`** [@kableExtra]: Enhanced table styling and
    formatting for clean, professional presentations.
-   **`ggalt`** [@ggalt]: Allowed the creation of specialized plots,
    enhancing the depth of data visualizations.
-   **`haven`** [@haven]: Facilitated the import of `.sav` survey data
    from the Afrobarometer.
-   **`broom.mixed`** [@broommixed]: Streamlined the extraction and
    tidying of results from mixed models for easy analysis and
    visualization.
-   ***Telling Stories with Data*** [@tellingstories]: This book was
    referenced for its code and methodologies.

## Cleaned Data Overview

```{r}
#| label: tbl-cleaned-data-preview
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| tbl-cap: "Preview of the Cleaned Dataset"

@@

The cleaned dataset used in this study is summarised in
@tbl-summary-statistics, which provides key statistics to offer an
overview of the dataset's structure and characteristics. The most
frequent age group among respondents is identified, representing the
predominant demographic in terms of age. The table also highlights the
urban and male percentages, which indicate the proportion of urban
residents (43.38%) and male respondents (49.68%) in the sample.

@@

## Corruption Perceptions Vs Variables of Interest

```{r}
#| label: fig-education-vs-corruption
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| fig.cap: "Relationship between Education Levels and corruption percetpions in Nigeria  in Nigeria"

@@

This heatmap in @fig-education-vs-corruption shows the relationship
between respondents’ education levels and their perceptions of
corruption in Nigeria. The data reflects responses to the question:
*What is your highest level of education?*.The x-axis represents
corruption perception categories (All Corrupt, High Corruption, No
Corruption, and Some Corruption), while the y-axis represents education
levels, ranging from No Formal Schooling to Post-graduate. The intensity
of the color reflects the number of respondents, with darker shades
indicating higher counts.

The heatmap reveals that respondents who completed secondary school or
some secondary schooling dominate the High Corruption and Some
Corruption categories. Respondents with higher education levels
(university and post-graduate) are distributed more evenly across the
corruption perception categories, with fewer concentrated in any
specific category. Conversely, respondents with no formal schooling or
only informal education are sparsely represented across all
categories.There is a notable concentration of corruption perceptions
among respondents with mid-level education (secondary schooling), while
those with higher education tend to have more varied perceptions. These
findings suggest a potential link between educational attainment and
experiences or attitudes toward corruption, particularly among those
with secondary-level education.

@@

@fig-age-versus-corruption shows the relationship between respondents'
age group which was obtained by asking the respondent *How old are you?* and their perceptions of corruption in Nigeria. Each panel corresponds to one of four corruption perception levels. Within
each panel, the bars represent the count of respondent across five age
groups (18-24, 25-34, 35-44, 45-54, and 55+), enabling a clear
comparison of how perceptions vary by age.

The 25–34 and 35–44 age groups have the highest counts in the High
Corruption and Some Corruption categories, suggesting that middle-aged
respondents are more likely to perceive corruption as significant. In
contrast, younger respondents (18–24) and older respondents (55+) report
lower levels of corruption perception in these categories.In the All Corrupt category, the 25–34, 35–44, and 55+ age groups dominate, while the 18–24 and 45–54 groups have lower counts. The No
Corruption category has low counts across all age groups, indicating
that very few respondents, regardless of age, perceive the absence of
corruption.

@@

# Convert corruption_presidency to numeric 
cleaned_data$corruption_numeric <- as.numeric(factor(cleaned_data$corruption_presidency))

The relationship between respondents' residential location (rural vs.
urban) and their perceptions of corruption is shown in
@fig-ruralurban-versus-corruption Each bar represents the proportion of
respondents within rural and urban groups who hold different corruption
perceptions.

@@

Residential location does not significantly influence corruption perceptions, as
rural and urban respondents report similar distribution patterns across all 
categories. The results suggest that perceptions of corruption are pervasive and
relatively consistent across geographic locations.

@@

@fig-gender-versus-corruption shows the the relationship between
respondents' gender (male and female) and their perceptions of
corruption. Each panel represents one gender, displaying the count of
respondents across four corruption perception categories: All Corrupt,
High Corruption, Some Corruption, and No Corruption.

@@

@@

# Results {#sec-results}

@@

The analysis revealed distinct trends in Corruption perceptions in
different demographics. Our results are summarized in @tbl-modelresults. 
This presents the estimated coefficients and standard
errors for each predictor included in the model. The dependent variable
is the perception of corruption in the presidency, categorized into
ordered levels. The table includes predictors such as education level,
gender, urban or rural location, and agre group, which are modeled to
explain variations in corruption perceptions. Each predictor's
coefficient represents its effect on the log odds of perceiving
corruption in the presidency at a specific level relative to lower
levels, holding other variables constant.

@@

# Discussion {#sec-discussion}

This paper looks into the demographic disparities of corruption
perception in the Nigerian presidency, using survey data to examine
variables like education, gender, age and urban versus rural residence.
By looking at these factors, the study aims to inform targeted
anti-corruption camapigns and policy making. The Bayesian modeling
approach helps us understand the relationship between corruption
perceptions and these demographic variables.

## Tareting Education Levels in Anti-Corruption Campaigns {#sec-first-point}

The relationship between education and corruption perceptions shows that
respondents with secondary school education are the most likely to
perceive high levels of corruption in the presidency. This supports
broader research showing that moderate levels of education are linked to
increased political awareness and accountability demands, as individuals
in this group are better equipped to identify systemic corruption but
may lack the structural access to address it effectively
[@transparency2019]. Individuals with higher education, such as
university graduates, report more moderate corruption perceptions, this
might largely beceause of their exposure to diverse viewpoints and
greater access to institutional frameworks that allow for political
skepticism. These suggest that anti-corruption campaigns targeting this
moderately educated demographic should focus on actionable reforms and
accountability mechanisms to harness their heightened awareness
productively [@u4nigeria2023].

## Urban-Rural Dynamics in Perception

Urban respondents are somewhat more likely than their rural counterparts
to perceive high corruption in the presidency. This is consistent with
findings that urban populations have greater access to investigative
reporting and public discourse on corruption, which can amplify
awareness and perceptions [@u4nigeria2023]. On the other hand, rural
respondents, who may rely on localized patronage networks for essential
services, often exhibit more neutral or unclear perceptions of
corruption, influenced by limited media access and dependency on these
informal systems. Campaigns should focus on leveraging urban platforms
like social media, community-based programs, and public dialogues to
engage critical urban audiences, while also expanding rural outreach
through local radio, grassroots organizations, and educational
interventions tailored to these settings.

## The Role of Age, Youth & Gender Engagement

Younger respondents, particularly those aged 25–34, consistently report
higher perceptions of corruption compared to older age groups. This
aligns with existing research that highlights younger demographics as
more vocal in their demands for systemic change in a country like
Nigeria, where over 60% of the population is under 25 [@UNFPA2023],
targeted anti-corruption initiatives that harness youth energy are
important. These efforts should include digital campaigns on platforms
frequently used by younger audiences, interactive town hall discussions,
and youth-led advocacy initiatives that focus on transparency and
accountability. Importantly, such campaigns need to have clear pathways
for action, making it easy for youth to channel their frustration into
productive engagement with governance structures.

While gender differences in corruption perceptions were less pronounced
in our paper, prior research shows that women often experience
corruption indirectly, particularly in accessing healthcare or education
systems [@GenderCorruption2021]. This shows the need for anti-corruption
campaigns that address systemic barriers disproportionately impacting
women, emphasizing institutional reforms in sectors that are important
to gender equity. Moreover, trust in institutions plays an important
role in shaping perceptions. Corruption scandals and perceived impunity
have a way of eroding trust, particularly in urban areas where political
engagement is higher[@afrobarometer2007]. Restoring institutional
credibility through transparency and consistent enforcement of
anti-corruption measures can increase the effectiveness of campaigns
targeting both genders.

@@

This paper is focused on looking at trends in the corruption perception
between different demographics and seeing how these differences can be
leveraged to maximize anti corruption campaigns and policy in
Nigeria.From this paper, we find different actionable strategies for
improving the effectiveness of anti-corruption campaigns in Nigeria.
First, targeting rural and urban populations differently might be
effective. Urban residents, who have greater access to investigative
media and public debates, are more likely to perceive high corruption.
Campaigns in urban areas should therefore focus on digital platforms
like social media and mobile apps, as well as partnerships with
investigative journalists and public accountability platforms to engage
this group effectively. In rural areas, where reliance on patronage
systems and limited media access shape perceptions, grassroots
communication strategies like community radio, local town halls, and
collaborations with trusted community leaders are better suited to
disseminate anti-corruption messaging.

Education also emerges as a key determinant of corruption perceptions.
Secondary school graduates exhibit the highest levels of awareness, this
suggests that civic education campaigns should focus on this demographic
to harness their increased engagement. Integrating anti-corruption
education into school curricula could early awareness and long-term
attitudinal changes.Youth engagement is very important, given that
younger age groups, particularly those aged 25–34, report the highest
levels of dissatisfaction with corruption. Social media campaigns
tailored to platforms popular with youth, together with interactive town
hall discussions and youth-led grassroots initiatives, could channel
this demographic's energy into organized anti-corruption efforts.

Lastly, rebuilding public trust in institutions should be a priority.
Transparent hiring practices, visible enforcement of anti-corruption
laws, and strengthened whistleblower protections are important steps to
showing institutional accountability. Localized outreach through
community leaders can also help bridge the trust gap, particularly in
rural settings. Policymakers should put these findings into a
data-driven framework so they can adapt strategies based on demographic
trends and feedback.

@@

While this paper tells us a lot about the demographic distributions of
corruption perception about the presidency in Nigeria, there are a few
limitations that have to be considered. The survey data relies on
self-reported perception, which can be influenced by social desirability
bias which refers to the situation where respondents' endorse more
favorable responses in order to enhance their own
self-presentation[@bias2022].For example, high-profile corruption
scandals or electoral promises happening close to survey periods may
distort responses. The data does not account for regional differences
within these urban rural classifications, which could change the
understanding of corruption perceptions further.The last limitation is
with the bayesian model, because while the Bayesian model accounts for
uncertainty, it does not address potential unobserved variables, like
political affiliations or socioeconomic status, which may affect the
relationships we say.

Future research should look more into longitudinal trends in corruption
perceptions to look at how demographic factors evolve over time. This
could be achieve through tracking respondents across electoral cycles or
policy interventions to observe shifts in attitudes. Additionally,
looking more into regional subcategories could show us some localized
patterns, particularly in states that have different governing
structures and resource allocation systems. Expanding the dataset to
include qualitative information from interviews and focus groups would
also give more information about how demographic characteristics relate
to peoples' lived corruption experiences.

@@

# Surveys, Sampling, and Observational Data {#sec-survey-appendix}

## Survey Methodolgy and Design

## Sampling Techniques

## Observational Data Challenges

## Proposed Improvements

@@

![Combined plot](combined_plot.png){width="120%"}

@@

# Posterior Predictive Check
pp_check(bayesian_model) +
  theme_classic() +
  labs(
    title = "Posterior Predictive Check",
    x = "Observed Data",
    y = "Density"
  ) + 
  scale_x_continuous(
    name = "Observed Data",     
    breaks = seq(0, 1, by = 0.1), 
    limits = c(1.1, 2.8)             
  )

@@
